\begin{thebibliography}{}

\bibitem[Altman y Bland(1995)]{altman1995}
Altman, D.~G. y Bland, J.~M. (1995).
\newblock Statistics notes: absence of evidence is not evidence of absence.
\newblock {\em BMJ}, 311:485.

\bibitem[Beigel et~al.(2024)Beigel, Packer, Gallardo, y Salatino]{beigel2024}
Beigel, F., Packer, A.~L., Gallardo, O., y Salatino, M. (2024).
\newblock OLIVA: La Producción Científica Indexada en América Latina.
\newblock {\em DADOS}, 67(1):e20210174.

\bibitem[D'Arrigo et~al.(2024)D'Arrigo, Abd El Hafeez, Mezzatesta, Abelardo, Provenzano, Vilasi, Torino, y Tripepi]{darrigo2024}
D'Arrigo, G., Abd El Hafeez, S., Mezzatesta, S., Abelardo, D., Provenzano, F.~P., Vilasi, A., Torino, C., y Tripepi, G. (2024).
\newblock Common mistakes in biostatistics.
\newblock {\em Clinical Kidney Journal}, 17(7):sfae197.

\bibitem[Farcomeni(2017)]{farcomeni2017}
Farcomeni, A. (2017).
\newblock Contribution to the discussion of the paper by Stefan Wellek: A critical evaluation of the current p-value controversy.
\newblock {\em Biometrical Journal}, 59(5):1066--1068.

\bibitem[Gelman y Stern(2006)]{gelman2006}
Gelman, A. y Stern, H. (2006).
\newblock The difference between ``significant'' and ``not significant'' is not itself statistically significant.
\newblock {\em The American Statistician}, 60(4):328--331.

\bibitem[Hoenig y Heisey(2001)]{hoenig2001}
Hoenig, J.~M. y Heisey, D.~M. (2001).
\newblock The abuse of power.
\newblock {\em The American Statistician}, 55(1):19--24.

\bibitem[Ioannidis(2005)]{ioannidis2005}
Ioannidis, J.~P.~A. (2005).
\newblock Why most published research findings are false.
\newblock {\em PLoS Medicine}, 2(8):e124.

\bibitem[Lang y Altman(2015)]{lang2015}
Lang, T.~A. y Altman, D.~G. (2015).
\newblock Basic statistical reporting for articles published in biomedical journals: The ``Statistical Analyses and Methods in the Published Literature'' or the {SAMPL} Guidelines.
\newblock {\em International Journal of Nursing Studies}, 52(1):5--9.

\bibitem[Mansournia y Nazemipour(2021)]{mansournia2021}
Mansournia, M.~A. y Nazemipour, M. (2021).
\newblock Recommendations for accurate reporting in medical research statistics.
\newblock {\em The Lancet}, 398(10313):1811.

\bibitem[Navarrete(2019)]{navarrete2019}
Navarrete, M.~S. (2019).
\newblock Ideas equivocadas frecuentes en estadística explicadas sencillamente.
\newblock {\em Medwave}, 19(6):e7660.

\bibitem[Noordzij et~al.(2010)Noordzij, Tripepi, Dekker, Zoccali, Tanck, y Jager]{noordzij2010}
Noordzij, M., Tripepi, G., Dekker, F.~W., Zoccali, C., Tanck, M.~W., y Jager, K.~J. (2010).
\newblock Sample size calculations: basic principles and common pitfalls.
\newblock {\em Nephrology Dialysis Transplantation}, 25:1388--1393.

\bibitem[Open Science Collaboration(2015)]{osc2015}
Open Science Collaboration (2015).
\newblock Estimating the reproducibility of psychological science.
\newblock {\em Science}, 349(6251):aac4716.

\bibitem[Peralta Díaz y Caldera Morillo(2023)]{peralta2023}
Peralta Díaz, V.~S. y Caldera Morillo, E.~J. (2023).
\newblock Calidad metodológica de artículos científicos como reportes de investigación en revistas estudiantiles venezolanas.
\newblock {\em Revista Ciencias de la Educación}, 33(61):13--38.

\bibitem[Reinhart(2015)]{reinhart2015}
Reinhart, A. (2015).
\newblock {\em Statistics Done Wrong: The Woefully Complete Guide}.
\newblock No Starch Press, San Francisco.

\bibitem[Schmidt(2025)]{schmidt2025}
Schmidt, A. (2025).
\newblock Addressing common inferential mistakes when failing to reject the null-hypothesis.
\newblock {\em F1000Research}, 13:1488.

\bibitem[Schulz et~al.(2010)Schulz, Altman, Moher, y CONSORT Group]{schulz2010}
Schulz, K.~F., Altman, D.~G., Moher, D., y CONSORT Group (2010).
\newblock CONSORT 2010 statement: updated guidelines for reporting parallel group randomised trials.
\newblock {\em BMJ}, 340:c332.

\bibitem[Thomas(1997)]{thomas1997}
Thomas, L. (1997).
\newblock Retrospective power analysis.
\newblock {\em Conservation Biology}, 11(1):276--280.

\bibitem[von Elm et~al.(2007)von Elm, Altman, Egger, Pocock, G\o{}tzsche, y Vandenbroucke]{vonelm2007}
von Elm, E., Altman, D.~G., Egger, M., Pocock, S.~J., G\o{}tzsche, P.~C., y Vandenbroucke, J.~P. (2007).
\newblock The Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) statement: guidelines for reporting observational studies.
\newblock {\em The Lancet}, 370(9596):1453--1457.

\end{thebibliography}
